Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2022-11-25 data_analysis.Rmd
Data analysis should be about finished

```{r packages, include = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
library(pander) # viewing AIC comparisons between models
library(AICcmodavg) # also helps viewing AIC comparisons
library(MuMIn) # to run the dredge function
library(lme4) # to run the glmer function for the web distance (random effects)
library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
```

@@

Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph. We also create another data set "sites" that restricts "webs" to just a single data point for each site. We use "sites" to compare search distance, the number of webs, and the number of spiders. We will use "webs" for web height and nearest neighbor analyses. The "web_dist" dataset looks at the distance from the focal web to the nearest and second nearest neighbors.

@@

web_dist <- webs %>% 
  filter(RetreatDist != 0,
         RetreatDist < 1000,
         Web == "W002" | Web == "W003") %>% 
  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
```

At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future. Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data; a second type of centering and scaling involves subtracting the median and dividing by the interquartile range; need to remember to back transform when making figures; we didn't scale and center because log-transformations on zero-inflated variables were enough to remove convergence errors

```{r sites_wrangling, include = FALSE}
sites <- sites %>% 
  mutate(patch_area_km = patch_area_mm * 1e-6)
```

@@

Many data are zero-inflated or right skewed. We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros. Echo = FALSE shows the results, but does not show the code used.

@@

# use as is, log won't work because some data are zero
ggplot(sites, aes(x = tree100m)) +
  geom_density()
shapiro.test(sites$tree100m) # not normal

@@

web_dist <- webs %>% 
  filter(RetreatDist != 0,
         RetreatDist < 1000,
         Web == "W002" | Web == "W003") %>% 
  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
```

@@

web_dist_forest <- web_dist %>% 
  filter(Location == "Urban Forest")
```

@@

corr <- sites %>% 
  select(TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway)
chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman

@@

corr_transformed <- sites %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m)

@@

corr_transformed <- sites %>% 
  select(log_TotalSub, log_tdr, log_tdh)
chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
```

@@

findCorrelation(cor(corr_forest, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# This suggests removing imperv100m, spec_rad, light_rad, road_length_m, and trail_length_m
# We will keep tree100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, and patch_area_km
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")
corr_forest <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, TotalSub, Traffic_Dist_Road, patch_area_km, Traffic_Dist_Highway)
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")

# Let's try with the log-transformed
corr_forest_transformed <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)

@@

corr_forest_transformed <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, log_TotalSub, log_tdr, patch_area_km, log_tdh)
chart.Correlation(corr_forest_transformed, histogram = TRUE, method = "spearman")
```

@@

# Let's try with the transformed
corr_center_transformed <- sites %>% 
  filter(Location == "Urban Center") %>% 
  select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)
findCorrelation(cor(corr_center_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
chart.Correlation(corr_center_transformed, histogram = TRUE, method = "pearson")
# The same variables are kept or removed
```

@@

predictions <- summary(emmeans(tree100m, ~Location),type = "response")

@@

Tree cover is *significantly higher in the urban forest* than the urban center (z = -14.50, df = 1, 20, p < 0.001). The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.

@@

predictions <- summary(emmeans(imperv100m, ~Location),type = "response")

@@

Impervious cover is *significantly higher in the urban center* than the urban forest (z = 14.51, df = 1, 20, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.

@@

predictions <- summary(emmeans(tdr, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = exp(log_tdr))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
  theme_classic() +
  ylab("Road Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=1400, label="", color="black", size = 10)
```

@@

There is *no difference* in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161). The means and SE's are 52.98 ± 1.88 vehicles/day/m for the urban forest and 194.42 ± 1.93 vehicles/day/m for the urban center.

@@

predictions <- summary(emmeans(tdh, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = exp(log_tdh))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_classic() +
  ylab("Highway Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=250, label="", color="black", size = 10)
```

@@

There is *no difference* in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596). The means and SE's are 33.78 ± 1.80 vehicles/day/m for the urban forest and 52.46 ± 1.77 vehicles/day/m for the urban center.

@@

predictions <- summary(emmeans(plant, ~Location),type = "response")

@@

Plant species richness is *significantly higher in the urban forest* than the urban center (z = -2.430, df = 1, 20, p = 0.015). The means and SE's are 12.18 ± 1.65 species for the urban forest and 2.97 ± 1.35 species for the urban center.

@@

predictions <- summary(emmeans(spec, ~Location),type = "response")

@@

Spectral radiance is *significantly higher in the urban center* than the urban forest (z = 3.079, df = 1, 20, p = 0.002). The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.

@@

predictions <- summary(emmeans(light, ~Location),type = "response")

@@

Light radiance is *significantly higher in the urban center* than the urban forest (z = 22.46, df = 1, 20, p < 0.001). The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.

@@

predictions <- summary(emmeans(patch, ~Location),type = "response")

@@

Patch area is *significantly higher in the urban forest* than the urban center (z = -3.599, df = 1, 20, p < 0.001). The means and SE's are 37,049.12 ± 2.80 mm^2 for the urban forest and 437.03 ± 2.03 mm^2 for the urban center.

@@

predictions <- summary(emmeans(road, ~Location),type = "response")

@@

Total road length is *significantly higher in the urban center* than the urban forest (z = 20.89, df = 1, 20, p < 0.001). The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.

@@

For this variable, I've been going back and forth on whether I should log-transform the search distance (because it can be ran Guassian), or whether to use a log-link function (Poisson Distribution). The poisson glm more closely matches the mean, but the log-transformation is better at capturing the variance. Each step of the way, I have performed each test to try and gauge a best route forward. The poisson glm suggests a significant difference while the log-transformed shows no difference.

@@

@@

*Overall*
Coefficients:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)   2.45699    0.24451  10.049  < 2e-16 ***
log_tdh       0.21434    0.04469   4.796 1.62e-06 *** *positive*
log_tdr       0.13279    0.01775   7.480 7.42e-14 *** *positive*
log_TotalSub  0.31671    0.03252   9.740  < 2e-16 *** *positive*

@@

*Urban Forest*
Coefficients:
              Estimate Std. Error z value Pr(>|z|)    
(Intercept)  -2.962190   0.608574  -4.867 1.13e-06 ***
log_tdh       1.354582   0.109952  12.320  < 2e-16 *** *positive*
log_tdr       0.718623   0.038386  18.721  < 2e-16 *** *positive*
log_TotalSub -1.010040   0.095179 -10.612  < 2e-16 *** *negative*
tree100m      0.049914   0.004241  11.770  < 2e-16 *** *positive*

@@

*Urban Center*
Coefficients:
              Estimate Std. Error z value Pr(>|z|)    
(Intercept)  -26.90656    2.78649  -9.656  < 2e-16 ***
log_patch      1.05254    0.05903  17.832  < 2e-16 *** *positive* 
log_tdh        0.58001    0.09128   6.354 2.10e-10 *** *positive*
log_tdr        0.45331    0.04386  10.335  < 2e-16 *** *positive*
log_TotalSub   0.54581    0.08135   6.709 1.96e-11 *** *positive*
spec_rad       0.12466    0.01458   8.549  < 2e-16 *** *positive*

@@

# Road Disturbance
nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
                 log_patch = mean(sites_center$log_patch),
                 spec_rad = mean(sites_center$spec_rad),
                 log_tdr = seq(3.00, 7.22, 0.04), 
                 log_tdh = mean(sites_center$log_tdh))
predicted.distance <- augment(top_model_sd_c, 
                              newdata = nd, 
                              se_fit = TRUE)
ggplot(sites_center, aes(x = log_tdr, y = log(WalkDist))) + 
  geom_point(color = "grey", 
             size = 1) +
  geom_line(aes(x = log_tdr, y = .fitted), 
            size = 1, 
            color = colorc, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_tdr, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorc, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
  theme_classic() +
  xlab("Road Disturbance [log(vehicles/day/m)]") +
  ylab("Search Distance [log(m)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()) +
  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)

@@

```{r search_land_stats}
search_land <- glm(WalkDist ~ Land, data = sites, family = poisson)
summary(search_land)
anova(search_land, test = "Chisq")
comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

@@

@@

# Log-transformed, Normal
test_webs2 <- augment(webs2, data = sites)
resid_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

@@

*Overall*
Coefficients:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)   7.55449    0.87254   8.658  < 2e-16 ***
log_tdh      -1.26833    0.19726  -6.430 1.28e-10 *** *negative*
log_tdr       0.18726    0.04729   3.960 7.49e-05 *** *positive*
log_TotalSub -1.02619    0.09768 -10.505  < 2e-16 *** *negative*

@@

*Urban Center*
Coefficients:
               Estimate Std. Error z value Pr(>|z|)    
(Intercept)   13.145965   1.236110  10.635  < 2e-16 ***
log_patch     -0.293327   0.113716  -2.579   0.0099 **  *negative*
log_tdh       -1.539660   0.190172  -8.096 5.67e-16 *** *negative*
log_TotalSub  -0.717109   0.183835  -3.901 9.59e-05 *** *negative*
road_length_m -0.022553   0.004713  -4.785 1.71e-06 *** *negative*

@@

(conditional average) 
               Estimate Std. Error Adjusted SE z value Pr(>|z|)    
(Intercept)   12.284984   1.481836    1.650697   7.442  < 2e-16 ***
log_patch     -0.293327   0.113716    0.137194   2.138 0.032513 *   *negative*
log_tdh       -1.560993   0.192352    0.229029   6.816  < 2e-16 *** *negative*
log_TotalSub  -0.659231   0.186648    0.218846   3.012 0.002593 **  *negative*
road_length_m -0.021230   0.004766    0.005608   3.786 0.000153 *** *negative*

@@

```{r webs_land_stats}
webs_land <- glm(NumWebs ~ Land, data = sites, family = poisson)
summary(webs_land)
anova(webs_land, test = "Chisq")
comp <- glht(webs_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

@@

@@

@@

*Overall*
Coefficients:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)    7.3234     1.1068   6.617 3.67e-11 ***
log_tdh       -1.1932     0.2785  -4.284 1.84e-05 *** *negative*
log_TotalSub  -0.9523     0.1370  -6.952 3.61e-12 *** *negative*

@@

```{r spiders_land_stats}
spiders_land <- glm(NumSpiders ~ Land, data = sites, family = poisson)
summary(spiders_land)
anova(spiders_land, test = "Chisq")
comp <- glht(spiders_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

@@

Convergence issues that need addressed.

>>>>

```{r packages, include = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
library(pander) # viewing AIC comparisons between models
library(AICcmodavg) # also helps viewing AIC comparisons
library(MuMIn) # to run the dredge function
library(lme4) # to run the glmer function for the web distance (random effects)
library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
library(multcomp) # for pairwise comparisons of land cover categories
```

@@

Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph. We also create another data set "sites" that restricts "webs" to just a single data point for each site. We use "sites" to compare search distance, the number of webs, and the number of spiders. We will use "webs" for web height. The "web_dist" data set is a subset of "webs" that looks at the distance from the focal web to the nearest and second nearest neighbors.

@@

web_dist <- webs %>% 
  filter(RetreatDist != 0,
         RetreatDist < 1000,
         Web == "W002" | Web == "W003") %>% 
  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))

near <- web_dist %>% 
  filter(Neighbor == 1)
```

At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future.

- Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data.

- A second type of centering and scaling involves subtracting the median and dividing by the interquartile range.

It's important to remember to back transform when making figures. We didn't scale and center because log-transformations on right-skewed variables were enough to remove convergence errors.

```{r sites_wrangling, include = FALSE}
sites <- sites %>% 
  mutate(patch_area_km = patch_area_mm * 1e-6,
         tree100m_frac = as.numeric(tree100m/100),
         imperv100m_frac = as.numeric(imperv100m/100))
```

@@

Many data are right-skewed. We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros. Echo = FALSE shows the results, but does not show the code used.

@@

# use as is, log won't work because some data are zero
ggarrange(ggplot(sites, aes(x = tree100m)) +
  geom_density(), ggplot(sites, aes(x = tree100m_frac)) +
  geom_density(), ncol = 2, nrow = 1)
shapiro.test(sites$tree100m) # not normal
shapiro.test(sites$tree100m_frac) # not normal

@@

web_dist <- webs %>% 
  filter(RetreatDist != 0,
         RetreatDist < 1000,
         Web == "W002" | Web == "W003") %>% 
  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))

near <- web_dist %>% 
  filter(Neighbor == 1)
```

@@

web_dist_forest <- web_dist %>% 
  filter(Location == "Urban Forest")

near_forest <- near %>% 
  filter(Location == "Urban Forest")

near_center <- near %>% 
  filter(Location == "Urban Center")
```

@@

corr <- sites %>% 
  dplyr::select(TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway)
chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman

@@

corr_transformed <- sites %>% 
  dplyr::select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m)

@@

corr_transformed <- sites %>% 
  dplyr::select(log_TotalSub, log_tdr, log_tdh)
chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
```

@@

findCorrelation(cor(corr_forest, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# This suggests removing imperv100m, spec_rad, light_rad, road_length_m, and trail_length_m
# We will keep tree100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, and patch_area_km
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")
corr_forest <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  dplyr::select(tree100m, TotalSub, Traffic_Dist_Road, patch_area_km, Traffic_Dist_Highway)
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")

# Let's try with the log-transformed
corr_forest_transformed <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  dplyr::select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)

@@

corr_forest_transformed <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  dplyr::select(tree100m, log_TotalSub, log_tdr, patch_area_km, log_tdh)
chart.Correlation(corr_forest_transformed, histogram = TRUE, method = "spearman")
```

@@

# Let's try with the transformed
corr_center_transformed <- sites %>% 
  filter(Location == "Urban Center") %>% 
  dplyr::select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)
findCorrelation(cor(corr_center_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
chart.Correlation(corr_center_transformed, histogram = TRUE, method = "pearson")
# The same variables are kept or removed
```

@@

predictions <- summary(emmeans(tree100m, ~Location),type = "response")
predictions

@@

Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 20, p < 0.001). The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.

@@

predictions <- summary(emmeans(imperv100m, ~Location),type = "response")
predictions

@@

Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 20, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.

@@

predictions <- summary(emmeans(tdr, ~Location),type = "response")
predictions

ggplot(sites, aes(x = Location, y = exp(log_tdr))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
  theme_classic() +
  ylab("Road Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=1400, label="N. S.", color="black", size = 10)
```

@@

There is **no difference** in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161). The means and SE's are `r exp(3.97)` ± `r exp(0.630)` vehicles/day/m for the urban forest and `r exp(5.27)` ± `r exp(0.663)` vehicles/day/m for the urban center.

@@

predictions <- summary(emmeans(tdh, ~Location),type = "response")
predictions

ggplot(sites, aes(x = Location, y = exp(log_tdh))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_classic() +
  ylab("Highway Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=250, label="N. S.", color="black", size = 10)
```

@@

There is **no difference** in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596). The means and SE's are `r exp(3.52)` ± `r exp(0.593)` vehicles/day/m for the urban forest and `r exp(3.96)` ± `r exp(0.574)` vehicles/day/m for the urban center.

@@

predictions <- summary(emmeans(plant, ~Location),type = "response")
predictions

@@

Plant species richness is **significantly higher in the urban forest** than the urban center (z = -2.430, df = 1, 20, p = 0.015). The means and SE's are `r exp(2.50)` ± `r exp(0.500)` species for the urban forest and `r exp(1.09)` ± `r exp(0.302)` species for the urban center.

@@

predictions <- summary(emmeans(spec, ~Location),type = "response")
predictions

@@

Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 20, p = 0.002). The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.

@@

predictions <- summary(emmeans(light, ~Location),type = "response")
predictions

@@

Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 20, p < 0.001). The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.

@@

predictions <- summary(emmeans(patch, ~Location),type = "response")
predictions

@@

Patch area is **significantly higher in the urban forest** than the urban center (z = -3.599, df = 1, 20, p < 0.001). The means and SE's are `r exp(10.52)` ± `r exp(1.026)` mm² for the urban forest and `r exp(6.08)` ± `r exp(0.712)` mm² for the urban center.

@@

predictions <- summary(emmeans(road, ~Location),type = "response")
predictions

@@

Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 20, p < 0.001). The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.

@@

For this variable, I've gone back and forth on whether I should log-transform the search distance (because it can be ran Gaussian), or whether to use a log-link function (Poisson Distribution). The poisson glm more closely matches the mean, but the log-transformation is better at capturing the variance. Each step of the way, I have performed each test to try and gauge a best route forward. The poisson glm suggests a significant difference while the log-transformed shows no difference.

@@

Using a Poisson distribution, we **searched significantly further at sites in the urban forest** than the urban center to reach the focal web (z = -10.1, df = 1, 20, p < 0.001).

@@

*Overall*
Coefficients:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)   2.45699    0.24451  10.049  < 2e-16 ***
log_tdh       0.21434    0.04469   4.796 1.62e-06 *** **positive**
log_tdr       0.13279    0.01775   7.480 7.42e-14 *** **positive**
log_TotalSub  0.31671    0.03252   9.740  < 2e-16 *** **positive**

@@

*Urban Forest*
Coefficients:
              Estimate Std. Error z value Pr(>|z|)    
(Intercept)  -2.962190   0.608574  -4.867 1.13e-06 ***
log_tdh       1.354582   0.109952  12.320  < 2e-16 *** **positive**
log_tdr       0.718623   0.038386  18.721  < 2e-16 *** **positive**
log_TotalSub -1.010040   0.095179 -10.612  < 2e-16 *** **negative**
tree100m      0.049914   0.004241  11.770  < 2e-16 *** **positive**

@@

*Urban Center*
Coefficients:
              Estimate Std. Error z value Pr(>|z|)    
(Intercept)  -26.90656    2.78649  -9.656  < 2e-16 ***
log_patch      1.05254    0.05903  17.832  < 2e-16 *** **positive** 
log_tdh        0.58001    0.09128   6.354 2.10e-10 *** **positive**
log_tdr        0.45331    0.04386  10.335  < 2e-16 *** **positive**
log_TotalSub   0.54581    0.08135   6.709 1.96e-11 *** **positive**
spec_rad       0.12466    0.01458   8.549  < 2e-16 *** **positive**

@@

# Road Disturbance
nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
                 log_patch = mean(sites_center$log_patch),
                 spec_rad = mean(sites_center$spec_rad),
                 log_tdr = seq(3.00, 7.22, 0.04), 
                 log_tdh = mean(sites_center$log_tdh))
predicted.distance <- augment(top_model_sd_c, 
                              newdata = nd, 
                              se_fit = TRUE)
search_center_tdr <- ggplot(sites_center, aes(x = log_tdr, y = log(WalkDist))) + 
  geom_point(color = "grey", 
             size = 1) +
  geom_line(aes(x = log_tdr, y = .fitted), 
            size = 1, 
            color = colorc, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_tdr, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorc, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
  theme_classic() +
  xlab("Road Disturbance [log(vehicles/day/m)]") +
  ylab("Search Distance [log(m)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()) +
  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)

@@

```{r search_land_stats}
search_land <- glm(WalkDist ~ Land, data = sites, family = poisson)
summary(search_land)
car::Anova(search_land, test.statistic = "LR")
comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

@@

**Search distance significantly varies** by land class (Chi = 340.32, df = 4, p < 0.001).

@@

# Log-transformed, Normal
test_webs2 <- augment(web2, data = sites)
resid_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

@@

There were **significantly more webs at sites in the urban center** than the urban forest (z = 8.556, df = 1, 20, p < 0.001).

@@

*Overall*
Coefficients:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)   7.55449    0.87254   8.658  < 2e-16 ***
log_tdh      -1.26833    0.19726  -6.430 1.28e-10 *** **negative**
log_tdr       0.18726    0.04729   3.960 7.49e-05 *** **positive**
log_TotalSub -1.02619    0.09768 -10.505  < 2e-16 *** **negative**

@@

*Urban Center*
Coefficients:
               Estimate Std. Error z value Pr(>|z|)    
(Intercept)   13.145965   1.236110  10.635  < 2e-16 ***
log_patch     -0.293327   0.113716  -2.579   0.0099 **  **negative**
log_tdh       -1.539660   0.190172  -8.096 5.67e-16 *** **negative**
log_TotalSub  -0.717109   0.183835  -3.901 9.59e-05 *** **negative**
road_length_m -0.022553   0.004713  -4.785 1.71e-06 *** **negative**

@@

(conditional average) 
               Estimate Std. Error Adjusted SE z value Pr(>|z|)    
(Intercept)   12.284984   1.481836    1.650697   7.442  < 2e-16 ***
log_patch     -0.293327   0.113716    0.137194   2.138 0.032513 *   **negative**
log_tdh       -1.560993   0.192352    0.229029   6.816  < 2e-16 *** **negative**
log_TotalSub  -0.659231   0.186648    0.218846   3.012 0.002593 **  **negative**
road_length_m -0.021230   0.004766    0.005608   3.786 0.000153 *** **negative**

@@

```{r webs_land_stats}
webs_land <- glm(NumWebs ~ Land, data = sites, family = poisson)
summary(webs_land)
car::Anova(webs_land, test.statistic = "LR")
comp <- glht(webs_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

@@

The **number of webs significantly varies** by land cover class (chi = 106.67, df = 4, p < 0.001).

@@

The **number of spiders present by site is significantly higher in the urban center** (z = 4.863, df = 1, 20, p < 0.001).

@@

*Overall*
Coefficients:
             Estimate Std. Error z value Pr(>|z|)    
(Intercept)    7.3234     1.1068   6.617 3.67e-11 ***
log_tdh       -1.1932     0.2785  -4.284 1.84e-05 *** **negative**
log_TotalSub  -0.9523     0.1370  -6.952 3.61e-12 *** **negative**

@@

```{r spiders_land_stats}
spiders_land <- glm(NumSpiders ~ Land, data = sites, family = poisson)
summary(spiders_land)
car::Anova(spiders_land, test.statistic = "LR")
comp <- glht(spiders_land, linfct = mcp(Land = "Tukey"))
summary(comp)
```

@@
